{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update GPM TeX slide

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Filamentary transport in high-power H-mode conditions and in
  no/small-ELM regimes to predict heat and particle loads on PFCs for
  future devices}}
\date{{\footnotesize 14 November 2017}}
\author[N. Vianello and V. Naulin]{N. Vianello, V. Naulin for Topic-21
Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}
\textbf{Include scientific team and logos}
\end{frame}

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$
\item \only<2>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenarion in high-density NBH heated plasma on TCV has been established
}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
        images coupled with values of density and temperature at the
        target suggest a larger   
      \item<7|only@7> AUG: At all the current a clear roll-over in
        peak density observed and we can also track the radiation
        front move away from target earlier in density at lower current
      \item<8|only@8> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<9|only@9> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        whereas upstream profile modification at TCV are only observed
        well after rollover
      \item<10|only@10> AUG: There is the tendency towards larger blobs
        at lower current
      \item<11|only@11> TCV: this is not confirmed for TCV but in line
        with the lack of shoulder and detachment
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}

>>>>

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Filamentary transport in high-power H-mode conditions and in
  no/small-ELM regimes to predict heat and particle loads on PFCs for
  future devices}}
\date{{\footnotesize 14 November 2017}}
\author[N. Vianello and V. Naulin]{N. Vianello, V. Naulin for Topic-21
Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific Team}
\begin{center}
  Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum
\end{center}
\end{frame}

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<2>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenario in high-density NBH heated plasma on TCV has been established
}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \includegraphics<2>[height=.81\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GPI_blobs_AUG}}
    \centering{\includegraphics<12>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape. 
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing
        rates for intermediate and higher current (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        has been used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior. 
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
        cameras coupled with values of density and temperature at the
        target suggest a larger neutral density at lower current (even
        with comparable values of edge electron density)
      \item<7|only@7> AUG: At all the current a clear roll-over in
        peak density observed and we can also track the radiation
        front move away from target earlier in density at lower current
      \item<8|only@8> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<9|only@9> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        \alert{whereas upstream profile modification at TCV are only observed
        well after rollover}
      \item<10|only@10> AUG: There is the tendency towards larger blobs
        at lower current at all values of $\Lambda_{div}$
      \item<11|only@11> AUG: This need to be further confirmed
        independently by GPI measurements. The present setup allows
        for space resolution of the order of mm with a 397 kframe/s
        sampling rate. Small amount of He gas flux needed ($\sim
        1.5e^{17} atoms/ms$)
      \item<12|only@12> TCV: this is not confirmed for TCV where blob
        sizes is rather constant over a rather large range of
        $\Lambda_{div}$. At the same time we do not observe target
        density rollover neither upstream profile flattening 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
